Constant Error Tolerance Computational Fuzzy Extractors

### 2014-02-08 constantRate/ConstCompFuzzExt.tex

Both constructions are based on  obfuscation of point programs~\cite{canetti1997towards}.  A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.  Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.  For a point program, this means hiding all partial information about the point $w$. 
We need a strong version of point obfuscation, which is secure under composition.  
However, even for this strong version, obfuscation of point programs is much simpler and more efficient than general obfuscation \lnote{omer, could you put in some references?}. In particular, it is achievable under particular number-theoretic assumptions~\cite{bitansky2010strong}. It can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1998perfectly}.\bnote{ran or omer, is this a reasonable statement?}

>>>>

Both constructions are based on  obfuscation of point programs~\cite{canetti1997towards}.  A point program $I_w(x)$ outputs $1$ if $x=w$ and $0$ otherwise.  Intuitively, an obfuscated version of a program reveals nothing past its input and output behavior.  For a point program, this means hiding all partial information about the point $w$.
We need a strong version of point obfuscation that remains secure even when several obfuscations of correlated points are composed. While the standard definition of obfuscation \cite{barak2001possibility} does not imply security under composition, we can base our construction on the relaxed notion of \emph{virtual grey-box} obfuscation introduced in~\cite{bitansky2010strong}. For this notion, \cite{bitansky2010strong} construct composable obfuscation of point programs under particular number-theoretic assumptions. Additionally, such obfuscation can be made very efficient under a strong assumption on cryptographic hash functions~\cite{canetti1997towards}. We note that the problem of fuzzy extractors remains non-trivial even given the recent progress on general purpose obfuscation \cite{GargGH0SW13,BrakerskiR13,BarakGKPS13}, as the achieve notions of obfuscation seem to be insufficient.
